Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/appendix.tex
small fixes

     Consider the B2B model from equation \ref{eq:model} $$Y = (XE + N)F$$ with $N$ centred and full rank noise.

     If $F$ and $X$ are full-rank on $Img(E)$, then, the solution of B2B, $\hat H$ minimizes

     $$\min_H  \left \| X - XH\right\| ^2  + \left \| NH\right \| ^2$$ and satisfies

@@

Instead, we treat the binarization of $\hat{H}$ as a clustering problem: separate the elements in the diagonal into a group of ``small values'', and a group of ``large values''. More specifically, we propose to maximize the ratio of inter-group variance and to minimize the intra-group variance, over all possible splits of the diagonal into $p$ largest values and $d_x-p$ smallest values.
%
Letting $m_0$ and $m_1$ be the average values of the two clusters, $p$ and $d_x-p$ their size, and $v$ the total variance of the sample, we select the split maximizing the Sonquist-Morgan \citep{sonquist_morgan} \citep{kass75} criterion $\frac{p(d_x-p)}{d_x} \frac{(m_1 - m_0)^2}{v}$.
%
To binarize $\hat{H}$, set to one all the $p$ diagonal entries belonging to the ``large values'' group in the decided split, and setting to zero the rest of the $d_x-p$ diagonal entries.

>>>>

     Consider the B2B model from Equation $$Y = (XE + N)F$$ $N$ centred and full rank noise.

     If $F$ and $X$ are full-rank on $Img(E)$, then, the solution of B2B, $\hat H$, will minimise

     $$\min_H  \left \| X - XH\right\| ^2  + \left \| NH\right \| ^2$$ and satisfy

@@

Instead, we treat the binarization of $\hat{H}$ as a clustering problem: separate the elements in the diagonal into a group of ``small values'', and a group of ``large values''. More specifically, we propose to maximize the inter-group variance and to minimize the intra-group variance, over all possible splits of the diagonal into $p$ largest values and $d_x-p$ smallest values.
%
Letting $m_0$ and $m_1$ be the average values of the two clusters, $p$ and $d_x-p$ their size, and $v$ the total variance of the sample, we select the split maximizing the Sonquist-Morgan \citep{sonquist_morgan} \citep{kass75} criterion $\frac{p(d_x-p)}{d_x} \frac{(m_1 - m_0)^2}{v}$.
%
To binarize $\hat{H}$, set to one all the $p$ diagonal entries belonging to the ``large values'' group in the decided split, and setting to zero the rest of the $d_x-p$ diagonal entries.
